Home Nighttime Cough Monitoring

### 2024-12-12 Lilah Melzer/cough_monitor_analysis.qmd
cough analysis new data

pull_date <- mdy("8/28/24")

@@

  "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Raw/Cough_w_TotalCounts_0824 - Cough_agg_w_count_0828.csv",

@@

>>>>

pull_date <- mdy("11/25/24")

@@

  "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor/Data_Raw/Cough_w_TotalCounts_1105 - Cough_agg_w_count_nov25.csv",

@@

agg_counts$`#nights-monitoring` = NULL
